\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=14pt, a4paper, french, english]{scrartcl}
%need to tell arXiv to process with pdflatex with the following line. Then, "Package hyperref Message: Driver (autodetected): hpdftex." Otherwise, urls don’t break, which messes the bibliography. See how to solve this (using latex?)
\pdfoutput=1
\input{preamble/packages}
\input{preamble/math_basics}
\input{preamble/math_mine}
\input{preamble/redac}
\input{preamble/draw}
\input{preamble/acronyms}

%\setbeamertemplate{headline}[singleline]

%printer margin: I take 0.5 inches = 1,27 cm to be safe. 21 cm - (2 × 1.27 cm) = 18.46 cm. 29.7 cm − 0.9 cm − (2 × 1.27 cm) = 26.26 cm
\areaset{18.46cm}{26.26cm}
\setlength{\footskip}{9mm}

\begin{document}
\title{%
	\texorpdfstring{
		The title%
		\thanks{
			This is an author version.
		}
	}{%
		A formal framework for deliberated judgment
	}
}
\author{Olivier Cailloux}
\author{Name2}
\affil{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 PARIS, FRANCE\\
	\href{mailto:olivier.cailloux@dauphine.fr}{olivier.cailloux@dauphine.fr}
}
\author{Name3}
\affil{Affil2}
\makeatletter
	\hypersetup{
		%do not use \subject, because appears on the page in article mode. Also, \keywords only defined in Beamer.
		pdfsubject={},
		pdfkeywords={},
		pdfauthor={Olivier Cailloux, }
	}
\makeatother
\maketitle

\section{Title with \electreTRI}
Text including \electreTRI.

\section{Font tests}
Try "some" \textbf{bold}, also some \textit{italic}, some \textsc{small caps}, some \textrm{roman}, some \texttt{mono}, some \url{mono-url}, some \textup{upshape}, and so on. Compare normal δ or b to math rm $\mathrm{\delta}$ or $\mathrm{b}$.
This link \url{http://tex.stackexchange.com/questions/31878/how-to-pass-definitions-to-atbegindocument} should break.

Some fractions in text: 1/2, 3/4, 10/12, and in math: $1/2$, $3/4$, $10/12$.

Try leq, ≤, in text.

Now for some math $m$, bold $\mathbf{b}$, some symbols\commentOC{This is a long comment in the middle.} $≤$ and $\mathbf{≤}$, reals $ℝ$ and $\mathbf{ℝ}$ (consider the bb $\mathbb{R}$, $\mathcal{R}$ and $\mathscr{R}$), vector $V$ and $\mathbf{V}$, set $S$ and $\mathcal{S}$, greek $\delta$ and $\mathbf{\delta}$, $\epsilon$ VS $\varepsilon$, $\phi$ VS $\varphi$, $\Phi$.

About special chars, what about $A \setminus B$, $a ∉ A$ (or $a \notin A$), $f \mapsto g$, a check $✓$ or in text ✓, or even $\lvert l\rvert$? What about the bold $\mathbf{a \notin b}$, $\mathbf{\lvert b\rvert}$, or $\mathbf{f \mapsto g}$?

I write \textsc{this part only} in SC shape.

Finally: \textbf{I write in bold now. And \textsc{now also in SC}, yeah man.}

{In this part, I suddently \texgyretermesfamily switch to \textbf{the Tex Gyre Termes 1/2 \textit{font} \textsc{including SC}}.}

%{In this part, I suddently \xitsfamily switch to \textbf{the XITS 1/2 \textit{font} \textsc{not including SC}}.}

\subsection{math bold}
\begin{itemize}
	\item mathcal: $\mathcal{L}, \mathcal{A}$
	\item mathbfcal: $\mathbfcal{L}, \mathbfcal{A}$ 
	\item mathscr: $\mathscr{L}, \mathscr{A}, 𝒜$
	\item mathbfscr: $\mathbfscr{L}, \mathbfscr{A}, 𝓐$.
\end{itemize}

\setmathfont{Latin Modern Math}
\setmathfont[range={\mathscr,\mathbfscr}]{XITS Math}
Using LM Math with XITS Math script.
\begin{itemize}
	\item mathcal: $\mathcal{L}$
	\item mathbfcal: $\mathbfcal{L}$ 
	\item mathscr: $\mathscr{L}$
	\item mathbfscr: $\mathbfscr{L}$.
\end{itemize}

%\bibliography{mybib}

\end{document}

